Exploring probability distributions for bivariate temporal granularities

### 2019-09-23 main.Rmd
idea 1: with good fielding( caught and caught and bowled, run rate decreases

@@

@@

 cricket_tsibble_all %>% 
  filter(season %in% c(2013, 2015), batting_team=="Mumbai Indians") %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

 cricket_tsibble_all %>% 
  filter(season %in% c(2013, 2015), batting_team=="Chennai Super Kings") %>% 
           granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")

>>>>

MI_winner %>% 
  gran_obs("win", "inning", hierarchy_model)

@@

CSK_winner %>% 
  gran_obs("win", "inning", hierarchy_model)

@@

MI <- cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015), batting_team=="Mumbai Indians")

CSK <- cricket_tsibble_all %>% 
  filter(season %in% c(2010:2015),
         batting_team=="Chennai Super Kings",
         inning %in% c(1,2))

 MI %>% 
   gran_obs("inning", "over", hierarchy_model) %>%
   knitr::kable(format = "markdown")

 CSK %>% 
   gran_obs("inning", "over", hierarchy_model) %>%
   knitr::kable(format = "markdown")

MI %>% 
  granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9))  + ggtitle("")

CSK %>% 
  granplot("inning", "over",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "lv",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9)) + ggtitle("")

### Overs in which fielding is good, run rate in that over is set ti reduce

```{r}
cricket_fielding <- cricket_season %>% 
  mutate(fielding_proxy = if_else(dismissal_kind %in% c("caught", "caught and bowled"),1,0)) %>% 
  group_by(season, match_id, batting_team, bowling_team,  inning, over) %>%
  summarise(runs_per_over = sum(total_runs), run_rate = sum(total_runs)/length(total_runs),
            fielding_wckts = sum(fielding_proxy))

cricket_tsibble_fld <- cricket_fielding %>% 
  ungroup() %>% 
  mutate(data_index = row_number()) %>% 
  as_tsibble(index = data_index)

cricket_tsibble_fld %>% gran_obs("over", "fielding_wckts")

cricket_tsibble_fld %>% 
  filter(fielding_wckts %in% c(0,1,2)) %>% 
  granplot( "over","fielding_wckts",
                               hierarchy_model,
                               response = "run_rate",
                               plot_type = "quantile",
                               quantile_prob = c(0.1, 0.25, 0.5, 0.75, 0.9),
           overlay = FALSE)  + ggtitle("")
